When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added exploratory results

---
title             : "When easy is not preferred: A discounting paradigm to assess load-independent task preference"
shorttitle        : "The CAD paradigm to assess task preference"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, credit.niso.org)
      - Conceptualization
      - Data curation
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role: 
      - Conceptualization
      - Resources
      - Supervision
      - Funding acquistion
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
abstract: |
  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
  We replicated the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Affective Discounting (CAD) Paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
  Results show that many participants preferred a more or the most difficult level.
  Variance in SVs was best explained by a declining logistic contrast of the $n$-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
  Participants with higher Need for Cognition scores perceived higher $n$-back levels as less effortful and found them less aversive.
  Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences mainly emerged in higher levels.
  The CAD Paradigm appears to be well suited for assessing and analysing task preferences independent of the supposed objective task difficulty.

@@

To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher $n$-back levels, we computed an rmANOVA with the within-factor level and the between-factor NFC group.
There was no main effect of NFC group (`r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`), but a main effect of the $n$-back level (`r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`) and an interaction (`r apa_print(explor_model)$full_result$nfcmedian_level`).
Post-hoc tests showed that

@@

Despite the visual separation of the SVs of participants with very low and high NFC scores in higher $n$-back levels, the NFC group did not reach significance in predicting SVs.
This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for $4$-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
This demonstrates that higher $n$-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.

@@

Effort and reward are two highly subjective concepts with relevance in daily life.
With each decision an individual makes, they must weigh the required effort against the expected reward to decide if and how to behave in that situation.
So far, effort discounting paradigms have relied on the assumption that the task that is objectively easiest is the one that is preferred by everyone, and each more difficult task is simply being devalued compared to the easy one.
However, effort-related traits such as Need for Cognition suggest that this is not the case.
Therefore, we developed a paradigm that allows effort discounting independent of objective task load, which we tested using an $n$-back task.
The results showed that many participants indeed preferred a more or even the most difficult $n$-back level.
Spanning the entire sample, these preferences took the shape of a declining logistic curve across $n$-back levels.
While the subjective value declined with increasing levels, it increased with better performance as measured in $d'$, and was unaffected by the reaction time.
Participants with Need for Cognition scores above the median reported lower subjective task load in and less aversion to more difficult levels.
However, they did not have higher subjective values per se, which was likely due to our choice of median split and our assumption that these group differences would emerge in lower levels.
In fact, the reaction time and self-report data suggest that individual differences emerge especially from 3-back upwards, emphasizing the need for a flexible effort discounting paradigm.
The CAD paradigm offers this flexibility, and we encourage future studies to question traditional assumptions in the field of effort discounting in the light of these findings, and to re-use this data set for exploratory analyses.

>>>>

---
title             : "When easy is not preferred: A discounting paradigm to assess load-independent task preference"
shorttitle        : "The CAD paradigm to assess task preference"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, credit.niso.org)
      - Conceptualization
      - Data curation
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role: 
      - Conceptualization
      - Resources
      - Supervision
      - Funding acquistion
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
abstract: |
  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
  We replicated the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Affective Discounting (CAD) Paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
  Results show that many participants preferred a more or the most difficult level.
  Variance in SVs was best explained by a declining logistic contrast of the $n$-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
  Participants with higher Need for Cognition scores perceived higher $n$-back levels as less effortful and found them less aversive.
  Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences only emerged in higher levels.
  The CAD Paradigm appears to be well suited for assessing and analysing task preferences independent of the supposed objective task difficulty.

@@

To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher $n$-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
There was no main effect of NFC group (`r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`), but a main effect of the $n$-back level (`r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`) and an interaction (`r apa_print(explor_model)$full_result$nfcmedian_level`).
Post-hoc tests for the main effect of level showed that Svs were lower for the more difficult $n$-back level in each paired contrast except for 1- versus 2-back.
Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (`r apa_print(pairs(explor_emm_interact))$full_result$X4_High_low`).
Despite not reaching significance, 1-back was the only level in which participants with NFC scores above the median seemed to have lower SVs than those with scores below the median (`r apa_print(pairs(explor_emm_interact))$full_result$X1_High_low`).
The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.

@@

Despite the visual separation of the SVs of participants with very low and high NFC scores in higher $n$-back levels, the NFC group did not reach significance in predicting SVs.
This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
As the exploratory analysis showed, only 4-back yielded a significant group difference, and SVs of participants with NFC scores above the median were higher for 2- to 4-back and lower for 1-back.
The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
This demonstrates that higher $n$-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.

@@

Effort and reward are two highly subjective concepts with relevance in daily life.
With each decision an individual makes, they must weigh the required effort against the expected reward to decide if and how to behave in that situation.
So far, effort discounting paradigms have relied on the assumption that the task that is objectively easiest is the one that is preferred by everyone, and each more difficult task is simply being devalued compared to the easy one.
However, effort-related traits such as Need for Cognition suggest that this is not the case.
Therefore, we developed a paradigm that allows effort discounting independent of objective task load, which we tested using an $n$-back task.
The results showed that many participants indeed preferred a more or even the most difficult $n$-back level.
Spanning the entire sample, these preferences took the shape of a declining logistic curve across $n$-back levels.
While the subjective value declined with increasing levels, it increased with better performance as measured in $d'$, and was unaffected by the reaction time.
Participants with Need for Cognition scores above the median reported lower subjective task load in and less aversion to more difficult levels.
However, they did not have higher subjective values per se, which was likely due to our choice of median split and our assumption that these group differences would emerge in lower levels.
In fact, the reaction time and self-report data suggest that individual differences emerge especially from 3-back upwards, emphasizing the need for tasks with high discriminatory power and effort discounting paradigms with flexible, participant-centered mechanisms.
The CAD paradigm offers this flexibility, and we encourage future studies to question traditional assumptions in the field of effort discounting in the light of these findings, and to re-use this data set for exploratory analyses.

### 2023-03-07 06_Paper/COG-ED/Stage 2/Supplement.Rmd
added exploratory results

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1a_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing $d'$ between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_mental_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_physical_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_time_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_performance_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_effort_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_frustration_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis2a_contrasts,
  caption = "Contrasts for the rmANOVA comparing the subjective values between $n$-back levels",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3a_contrasts_nlevel,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of subjective values",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3b_contrasts_levels,
  caption = "Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3b_contrasts_interact,
  caption = "Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores",
  note = "The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3c_contrasts_levels,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of aversiveness ratings",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3c_contrasts_nfc,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition (NFC) group and $n$-back level on difference scores of aversiveness ratings",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1a_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing $d'$ between $n$-back levels.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_mental_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between $n$-back levels.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_physical_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between $n$-back levels.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_time_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between $n$-back levels.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_performance_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between $n$-back levels.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_effort_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between $n$-back levels.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_frustration_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between $n$-back levels.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis2a_contrasts,
  caption = "Contrasts for the rmANOVA comparing the subjective values between $n$-back levels.",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3a_contrasts_nlevel,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of subjective values.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3b_contrasts_levels,
  caption = "Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3b_contrasts_interact,
  caption = "Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores.",
  note = "The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3c_contrasts_levels,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of aversiveness ratings.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3c_contrasts_nfc,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition (NFC) group and $n$-back level on difference scores of aversiveness ratings.",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

## Exploratory analyses

Main effect level: `r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`

Main effect NFC group: `r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`

Interaction: `r apa_print(explor_model)$full_result$nfcmedian_level`

Contrasts for main effect level:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  explor_contrasts_nlevel,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on subjective values.",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

Contrasts for the interaction:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  explor_contrasts_interact,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on subjectvie values.",
  note = "The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median. The column Level contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```
